Cross-lingual Document Similarity and Event Detection \todo{Better title...}

### 2015-03-03 rupnik2015.tex
outline added

\begin{abstract}
\todo{tralala hopsasa.}
\end{abstract}

>>>>

\begin{abstract}
\todo{tralala hopsasa.}
\end{abstract}
\section{Overview}
Structure
\begin{itemize}
\item Introduction
\item Cross lingual document similarity (model)
\item  Event Detection
\item  Combing the approaches
\item Experiments
\item Conclusions
\end{itemize}
The story:
\begin{itemize}
\item Description of the problem - we would liek to understand events ans sequences of events, but our observables (e.g. news stories) occur in a variety of languages
\item We present an approach to tackle this problem using a combination of techniques....
\item Ultimately we present a tool showing the feasibility of our approach
\end{itemize}
